---
title: "Final Project"
author: "Sean Palac"
date: "December 6, 2016"
output: 
  pdf_document: 
    fig_caption: true
---
```{r, echo = FALSE, include = FALSE}
library(xlsx)
library(acs)
library(ISLR)
library(blscrapeR)
library(dplyr)
library(choroplethr)
library(choroplethrMaps)
library(ggplot2)
library(leaps)
library(MASS)
library(knitr)
library(gam)
library(akima)

#Land Area per county
land <- read.xlsx("Land Area.xlsx", sheetIndex = 1)

#Employment/unemployment data
t = get_bls_county() 

#Personal Income data per county
economy = read.csv(file = "CA1_all_areas.csv")
```



```{r, echo = FALSE, include = FALSE}
#The following chunk is used to clean the data for age adjusted death rates due to heroin.
#This is done by taking our data set and first changing the name of our death rates column
#to something simple and easier to work with. Next, we change these rates to a numeric vector.
#From here we separate the two numbers from the dividing "-" in the data frame and find the 
#average of the amount of deaths that county faced that year, specifically 2014. I chose the
#average because it would be more representative than either the minimum or the maximum of the range given.
x <- read.csv("Drug_Poisoning_Mortality.csv")

names(x)[names(x) == "Estimated.Age.adjusted.Death.Rate..11.Categories..in.ranges."] <- "Deaths"


#Changing deaths from factors to numeric points. Below code given by Jacob (the TA)
x$Deaths <- as.character(x$Deaths)
temp <- strsplit(x$Deaths, split = "-") 

for (i in 1:length(temp)) {
    if(length(temp[[i]]) == 1){
      temp[[i]] <- 20
    }
  else if(length(temp[[i]]) == 2){
      temp[[i]] <- mean(as.numeric(temp[[i]]))
    }
}
  
x$Deaths <- unlist(temp)
heroin.2014 <- filter(x, Year == 2014)
```


```{r, echo = FALSE, include = FALSE}
#From Karl's demonstration on how to plot unemployment
api.key.install("34f30e784deb250daef6e59ea950f7ce8e8f38bd")

us.county=geo.make(state="*", county="*")
pop=acs.fetch(geography=us.county, 
              table.number="B01001", col.names="pretty", endyear = 2014)
tmp  = estimate(pop)
workingAgePop = rowSums(tmp[,c(7:15)]) #males from age 18 to 54 (i.e. working age men)

xpop = 
  as_data_frame(
    cbind(
      as.numeric(
        paste(
          as.character(pop@geography$state), 
          pop@geography$county, 
          sep="")), 
      workingAgePop)
    )


xpop = pop@geography %>% 
  transmute(fipsState = as.character(state), 
                            fipsCounty = county) %>% 
  transmute(fips = as.numeric(paste(fipsState, fipsCounty, sep = ""))) %>% 
  cbind(workingAgePop) 

colnames(xpop) = c("region", "population")

lmDat = t %>% 
  transmute(region = as.numeric(fips), labor_force= labor_force, unemployed_rate=unemployed_rate) %>% 
  right_join(xpop) %>% transmute(region = region, participation = labor_force/population, unemployed_rate = unemployed_rate)
```

```{r, echo = FALSE, include = FALSE}
economy.personal.income <- filter(economy, Description == "Per capita personal income (dollars) 2/")
wrong <- data.frame(economy.personal.income$X2014,economy.personal.income$GeoFIPS)
colnames(wrong) <- c("personal.income.2014", "fips")
wrong$fips <- as.numeric(as.character(wrong$fips))
wrong$personal.income.2014 <- as.numeric(as.character(wrong$personal.income.2014))
wrong=na.omit(wrong)

#Here, we join our dataframe of land area data with that of our heroin overdose statistics
this <- left_join(heroin.2014, land, by = c("FIPS" = "GEOID"))

#This will allow us to add a column to the newly made data frame where we divide the population
#of each county by the land area in square miles, giving us the population density of each
#county.
this["Pop.Density"] <- as.numeric(this$Population)/as.numeric(this$ALAND_SQMI)

#NA's cause problems when creating data frames to map, thus we omit them
this = na.omit(this)

#Here, we ensure that our common vector of fips codes are of the same type, numeric, in order
#to add our employment statistics to the aforementioned data frame, consolidating all our data.
#Once again, we omit any NA values from the dataframe.
t$fips <- as.numeric(t$fips)
this$FIPS <- as.numeric(this$FIPS)
unemployment_control <- left_join(this, t, by = c("FIPS" = "fips"))
unemployment_control <- na.omit(unemployment_control)

#Finally, we add our participation rate data per county to add our last control variable to the
#data frame, omitting any NA values that may have been added.
real <- left_join(unemployment_control, lmDat, by = c("FIPS" = "region"))
real = na.omit(real)

buhl <- left_join(real, wrong, by = c("FIPS" = "fips"))
buhl = na.omit(buhl)

#Counties with population densities over 5000 were removed from the data frames as they are 
#unrepresentative of much of the data and cause a lot of errors when creating plots and running 
#regressional analysis. They were far too influential to rely on the data
dude = which(buhl$Pop.Density>5000)

buhl = buhl[-c(dude),]

#Now we can condense all of our important information to a final dataframe for future ease.
final <- data.frame(as.numeric(buhl$FIPS), buhl$Deaths, buhl$Population, buhl$Pop.Density, buhl$labor_force, buhl$unemployed_rate.x, buhl$personal.income.2014)
colnames(final) <- c("fips", "deaths", "population", "pop.density", "labor force", "unemployment rate", "personal.income.2014")
final = na.omit(final)
levels(final$personal.income.2014)[1:9211]<-levels(final$deaths)

mapper <- data.frame(heroin.2014$Deaths, as.numeric(heroin.2014$FIPS))
colnames(mapper) <- c("value", "region")
```
##Introduction  
&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;The "War on Drugs" is a term popularized by former president Ronald Reagan. Recently, the main
focus of said war has been the legalization of marijuana. But one drug that has lurked in the
shadows and continues to become an ever-present threat to the American people, is heroin.
According to the Centers for Disease Control and Prevention, heroin use has more than doubled in
the past decade amongst American citizens. In addition, the US Department of Health and Human
Services has claimed that deaths related to heroin have more than tripled since 2010. Before we
can begin to address solutions to this problem, we must first discover where the problem is
manifesting. So the question remains: where is the recent spike in heroin use coming from? Is
the stereotypical belief that urban regions are the main contributor to drug use true, or has
the issue become the less populated, rural regions?  
&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;In order to answer the previously stated question, data tables were gathered with the intention
to gain information on the age adjusted death rates due to heroin as well as on population, land
area, and personal income statistics. All data sets were used to find data at the county level
in order to paint a more exact picture of the issue. From here, we use the population and land
area statistics to find the population densities of each county. The larger densities most
likely represent more populated, urban regions and the smaller densities most likely represent
the rural and suburban counties. Thus, we use these age adjusted death rates due to heroin use,
as predicted by the population density of counties and controlled for by economic factors such
as working age male participation rate, personal income, or unemployment rate to hypothesize
that the recent surge of heroin use is manifesting in the less dense, rural regions of America
rather than the more dense, urban counties. 
```{r,fig.cap="This maps the age adjusted rate of death per county across the US. This is to illustrate the main areas of concern in the country and to be used for comparison with later maps of residuals and fitted values of regressions. As we can see from the map, it seems that the west as well as the Appalachian Mountain area and Oklahoma are where the highest death rates seem to occur. However, the Midwest and New York have the lowest. This gives concern as to whether or not there is a regional effect or whether heroin has not penetrated the market in these areas.", fig.pos = "H", warning = FALSE}
county_choropleth(mapper, title = "Age Adjusted Death Rates 2014")
```
  
  
##Methods  
&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;The data used, begins with an evaluation of the Age Adjusted Death Rates for Drug Poisoning in
counties across the US. The data was gathered by the National Center for Health Statistics and
describes the estimated rate at which people in each county have died due to drug poisoning
causes. According to the NCHS, "Drug-poisoning deaths are defined as having ICD-10 underlying
cause-of-death codes X40-X44 (unintentional), X60-X64 (suicide), X85 (homicide), or Y10-Y14
(undetermined intent)." The recorded data spans from the year 1999 to 2014 and describes the
estimated range of age adjusted death rates rather than crude rates. Thus, in order to "clean"
the raw data uploaded, we must isolate that death rate data column, splitting the string value
where a "-" occurs. This is done in order to separate the minimum estimated rate of death
recorded and the maximum estimated rate of death per county. From here, we take the average of
the two values provided by the split in order to obtain the best estimation of the true age
adjusted death rate per county. We chose to record the average due to the assumption that
choosing the minimum or maximum rate estimations for each county would most likely tend to
provide an underestimated or overestimated prediction, respectively. In addition, choosing a
randomized value within the range would not be able to tell us much information, as the
randomization might not be truly representative of the county. Thus the "safest bet" is to use
the average of the two extremes. After replacing this ranged data with numerical averages for
each county across all years, we create a new data frame specifying the year of data desired. In
this case, the most recent year, 2014, was chosen as it would be most representative of current
trends in drug poisoning across the US.  
&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;Next, we upload the Bureau of Labor Statistics' (BLS) data on employment and unemployment rates
per county as well as the American Community Survey's (ACS) data available through R's packages.
From here, we are able to create a data frame of the working age population of specific
demographics as well as the fips codes of the counties they are associated with. This will be 
useful when paired with the BLS employment data as we can then combine the two data sets and
calculate the labor force participation of each county. For our research, we specifically looked
at the labor force participation of men aged 18 to 54 years old, as these ages represent the
prime working ages of American men. It was chosen to use these data due to the revelation of the
"Missing Men Phenomenon," which claims that there is a large group of working class men that are
missing from the labor force unlike previous decades. Due to surveys taken by different groups,
it is believed that injury and substance abuse, specifically with opioids, has led to this lack
of representation. Thus, in order to control for this clearly significant influence, we add the
participation rate as a control variable in our analysis.  
&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;In addition, data from the Bureau of Economic Analysis was used to acquire information about the
per capita personal income of a county. This was recorded for each county in order to control
for the possible confounding variable of poverty. Personal income is a measure of all the wealth
gained by a specific region in a given time period, which we will use as a proxy for wealth of a
county. I believe that for those with less personal income to spend, it can be assumed that it
would be harder to afford prescription painkillers and over-the-counter medicine to alleviate
pain. Thus, it can also be assumed that if heroin were to penetrate the market of these
lower-income areas, there would be a higher rate of heroin use and thus a higher rate of
heroin-related drug poisoning deaths. Therefore, in order to control for this possible
confounding variable, we add a variable for per capita personal income of each county to our
regression models.  
&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;Finally, we extracted data from the US Census Bureau on the land area and population statistics
of each county. From here, we combined the data frame on drug poisoning statistics, which also
included population counts of each county, with that of land area based on matching fips codes.
This allowed us to calculate the population density of each county by dividing the total
population of each county by its land area in square miles. Through this calculation, we created
a new column in the new data frame representing the desired densities, which was later used to
predict drug poisoning death rates. One issue that arose from this however, were outlying points
that had huge leveraging effects on our regression analysis. For instance, New York County had a
population density of approximately 70,000, which was well above the mean population density of
268. Thus, it was deemed necessary to remove rows of data that included population densities of
5000 or more, as they reduced the accuracy of our predictions, as well as their trustworthiness,
substantially.  





```{r, echo = FALSE, include = FALSE}
simple2 <- lm(final$deaths~final$pop.density+final$`labor force`)
summary(simple2)

simple3 <- lm(final$deaths~final$pop.density+final$`labor force`+final$pop.density*final$`labor force`)
summary(simple3)

simple4 <- lm(final$deaths~final$pop.density+final$`unemployment rate`)
summary(simple4)

simple5 <- lm(final$deaths~final$pop.density + final$personal.income.2014)
summary(simple5)

simple6 <- lm(final$deaths~final$pop.density+final$`unemployment rate`+final$pop.density*final$`unemployment rate`)
summary(simple6)

simple7 <- lm(final$deaths~final$pop.density+final$`labor force`+final$`unemployment rate`+final$pop.density*final$`unemployment rate`)
summary(simple7)

simple8 <- lm(final$deaths~final$pop.density+final$`labor force`+final$`unemployment rate`+final$personal.income.2014)
summary(simple8)

simple9 <- lm(final$deaths~final$pop.density+final$personal.income.2014+final$pop.density*final$personal.income.2014)
summary(simple9)
```

##Results 
```{r, echo = FALSE}
simple <- lm(final$deaths~final$pop.density)
summary(simple)
```
&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;The first test that was run was that of a simple linear regression, where our dependent variable
was the age adjusted death rates per county and our independent variable was population density.
Performing this regression with a single variable did give us a significant p-value of .0016
along with a beta coefficient of .0007146, which could suggest that population density does
indeed positively influence death rates due to heroin. The beta coefficient can be summed up to
mean that for each unit increase in population density, the death rate increases by .0007146.
Although this coefficient seems small, the amount at which population density may increase is
very large; thus, for population densities over 100, of which there are many, the death rate
will increase by quite a bit. However, I believe this correlation may occur due to the effects
of other confounding variables playing a part in the relationship between counties with large
population densities and high death rates. Thus, the variables unemployment rate, labor force,
and personal income were added to the model separately. In addition, interaction terms were
added to each respective model due the strong possibility of collinearity, especially in the
cases of unemployment rate and labor force. After running each simple regression and gathering
their respective p-values, all but two regression returned a p-value that indicated population
density was a significant determinant of average heroin death rates per county. The only
regressions that did not return similar findings were one that involved population density with
unemployment rate as well as an interaction term as independent variables and one with
population density and personal income as independent variables with an interaction term as
well. Thus, for simple linear regression models, we seem to have information pointing to the
idea that as population density increases, so does the age adjusted death rate due to heroin
use. However, when control variables are applied, it seems that population density is not very
predictive of death rates due to heroin use.  

```{r, fig2,echo=FALSE,warning=FALSE,fig.cap="As seen by the fact that our residuals plot contains seemingly parallel lines and how our Normal QQ plot has a pattern to it that does not follow a straight line, our independent variables must be correlated in some fashion. The parrallel lines following a downward sloping, linear pattern indicates to us that there are multiple classes of results and possibly that Linear Discriminant Analysis would be a better test for this data.", fig.pos="H"}
layout(matrix(c(1,2), 2, 2, byrow = TRUE))
plot(simple$fitted.values, simple$residuals, main = "Plotted Residuals for Initial Regression", xlab = "Residuals", ylab = "Fitted Values")
qqnorm(rstandard(simple))
```

```{r, fig3,echo=FALSE,warning=FALSE, fig.pos = "H", fig.cap="Here we have mapped the fitted values of our most accurate simple linear regression model. Based on how large these fitted values are in the given areas, we see that the model does not do the best at predicting death rates. In fact it overestimates nearly every region aside from those where heroin is a major issue, such as the Appalachian Mountain Range as well as the Southwest."}
map1 <- data.frame(simple6$fitted.values, as.numeric(final$fips))
colnames(map1) <- c("value", "region")
county_choropleth(map1, title = "Linear Model Fitted Values")
```

```{r, echo = FALSE, include = FALSE}
glm.fit = glm(final$deaths~final$pop.density+final$`unemployment rate`+final$pop.density*final$`unemployment rate`, family = "poisson")
summary(glm.fit)
```
&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;In addition to simple and multiple linear regression models, generalized linear modeling fit
with a Poisson distribution was attempted to find a truly influential independent variable. This
was a chosen method as our response variable only has a finite number of values it can return
based on our data cleaning. Thus, when we get our data, the average death rate due to heroin of
a county can be viewed as count data in a sense. Therefore, it was assumed that a regression fit
to a Poisson distribution would be more representative of the data collected than that of a
simple or multiple linear regression model. Thus, we found that the most representative model
for our data was that which regressed population density with unemployment rate and an
interaction term between the two. Once again, as was the case with our multiple regression,
unemployment rate seemed to be the significant variable, but population density was measured as
more significant in this case compared to the multiple linear regression test. Therefore, from
our fit model, we can determine that due to a large p-value of .152 associated to the population
density coefficient, population density is not a good predictor of the age adjusted death rate
due to heroin in a given county.  
```{r, echo = FALSE, warning = FALSE}
map5 <- data.frame(glm.fit$residuals, as.numeric(final$fips))
colnames(map5) <- c("value", "region")
```

```{r, fig4, warning = FALSE, echo = FALSE, fig.cap="Here, we have mapped the residuals to our Generalized linear regression model. We can see by the layout of the graph that there still seems to be a regional influence on the death rates estimated by our model. This can be seen by the consistency of certain residuals in each region, which implies correlated residuals. Ideally, we would expect the residuals to be more random throughout the nation and have more of a checkerboard pattern.", fig.pos="H"}
county_choropleth(map5, title = "Generalized Linear Model Residuals")
```

```{r, echo=FALSE, include = FALSE}
#g1 = gam(deaths~ lo(latitude, longitude, span = .2) + lo(pop.density) + lo(`unemployment rate`) + lo(`labor force`), data= final)
g1 = gam(deaths~ pop.density + `unemployment rate` + `labor force`, data= final)
summary(g1)

par(mfrow=c(1,4))
plot.gam(g1)
dev.off()
#residuals are no longer correlated
newmap <- data.frame(g1$residuals, final$fips)
colnames(newmap) <- c("value", "region")
county_choropleth(newmap, title = "Uncorrelated Residuals")

#Model consistently overestimates death rates
newmap2 <- data.frame(g1$fitted.values, final$fips)
colnames(newmap2) <- c("value", "region")
county_choropleth(newmap2)
```

&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;However, upon further inspection of the residual map, it was found that our residuals seem to be
very highly correlated. In particular, when checking the residual plot, there were distinct,
parallel lines with slopes of ~-1, seemingly based on the values associated with our average age
adjusted death rates data. In total, there were 11 different possibilities of death rates and 11
distinct lines in the residuals plot. Thus, after making this realization, Linear Discriminant 
Analysis tests were run. These tests are useful in determining whether our independent variables
are reasonable for predicting the dependent variable, especially in when distinct cases are
present, such as the 11 we see in our data. However, LDA does a better job of estimating
predictions for fewer cases, so for our second LDA, we designated three specific cases as
described later in the paragraph. First, was a basic LDA test with all four independent 
variables, population density, unemployment rate, personal income, and labor  participation. 
From this, we found that ~92% of explained "between-group" variance comes from the population 
density of a county, thus making it the variable that best explains variation in LDA.  After 
running a standard LDA regression with all variables and 11 classes to predict, we found that 
the LDA coefficients classify the death rate of a county correctly ~23% of the time. This value 
is found by summing all values along the diagonal of the table (i.e. the values predicted 
correctly) and dividing by the total number of predictions. In addition, we ran an LDA test 
where each death rate level was classified into a group: low, medium, and high. The bottom four 
values were classified as "low", the middle three as "medium", and the final four as "high". 
From here, another LDA test was run where the variables were to predict which category, low, 
medium, or high, a county would fall in in terms of death rate. This resulted in a correct 
classification ~53% of the time. Thus, we conclude that our independent variables do suffice in 
order to accurately predict the death rates of each county as they correctly classify the death 
rates of a county quite often considering how many possibilities there are.  
```{r, echo = FALSE, warning = FALSE}
r <- lda(final$deaths~final$pop.density+final$`unemployment rate`+final$`labor force`+final$personal.income.2014)

prop = r$svd^2/sum(r$svd^2)

r2 <- lda(final$deaths~final$pop.density+final$`labor force`+final$`unemployment rate`+final$personal.income.2014, CV = TRUE)

train <- sample(dim(final)[1], dim(final)[1]/2)

r3 <- lda(final$deaths~final$pop.density+final$`labor force`+final$`unemployment rate`+final$personal.income.2014, subset = train)

plda = predict(object = r, newdata = final[-train,c(3,4,5)])

tab <- table(plda$class, final$deaths)
kable(tab, caption = "LDA Prediction of Individual Death Rates")
```

```{r}
sum(diag(tab))/sum(tab)
#classifies correctly ~23%
```

```{r, echo = FALSE, warning = FALSE}
final$deaths[final$deaths == "1"] <- "low"
final$deaths[final$deaths == "3.05"] <- "low"
final$deaths[final$deaths == "5.05"] <- "low"
final$deaths[final$deaths == "7.05"] <- "low"
final$deaths[final$deaths == "9.05"] <- "medium"
final$deaths[final$deaths == "11.05"] <- "medium"
final$deaths[final$deaths == "13.05"] <- "medium"
final$deaths[final$deaths == "15.05"] <- "high"
final$deaths[final$deaths == "17.05"] <- "high"
final$deaths[final$deaths == "19.05"] <- "high"
final$deaths[final$deaths == "20"] <- "high"

r <- lda(final$deaths~final$pop.density+final$`unemployment rate`+final$`labor force`+final$personal.income.2014)

prop = r$svd^2/sum(r$svd^2)

r2 <- lda(final$deaths~final$pop.density+final$`labor force`+final$`unemployment rate`+final$personal.income.2014, CV = TRUE)

train <- sample(dim(final)[1], dim(final)[1]/2)

r3 <- lda(final$deaths~final$pop.density+final$`labor force`+final$`unemployment rate`+final$personal.income.2014, subset = train)

plda = predict(object = r, newdata = final[-train,c(3,4,5)])

tab2 <- table(plda$class, final$deaths)
kable(tab2, caption = "LDA Prediction of Grouped Death Rates")
```

```{r}
sum(diag(tab2))/sum(tab2)
#classifies data correctly ~54%
```
  
##Conclusions  
&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;Basing our conclusions on simple linear regression and multiple regression, if we were to ignore
the correlation between residuals, we would be able to conclude that population density does in
fact have a strong correlation with predicting the death rates due to heroin of each county.
However, these results indicated that as population density grew for a county, so did the
average rates of death. Therefore, if we relied solely on this data, it could be claimed that
more dense, urban areas are in fact the problem areas for the heroin epidemic, ultimately
rejecting our original hypothesis that rural regions were the main problem areas. However, once
other variables were added to our model, specifically unemployment, population density did very
little to determine these death rates. Therefore, it cannot be justifiably claimed that
population density explains an increase or decrease in age adjusted heroin death rates based off
of linear regression methods.  
&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;One limitation of running the initial regressions, however, was the fact that some of the 
explanatory variables seemed to be correlated to the other. This could be due to the fact that 
each can be explained or calculated by the total population of the county. Thus, finding less 
correlated variables could turn up new results and provide a stabilizing factor during simple linear regression.  
&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;Furthermore, when performing Forward Stepwise Selection, it was discovered that unemployment
rate seems to be more predictive than population density when death rates are regressed on
either. This could be because there is no true epicenter of the heroin epidemic in terms of
rural vs. urban locale but there is evidence to support the claim that being out of work
influences drug abuse. One possible explanation could be that those who are unemployed turn to
substance abuse to nurse the depression of being out of work, and the fact that they are out of
work means they must look for less expensive substances to consume.  
&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;Moreover, based on our more robust findings from LDA testing, which hampers the effect of
having a discrete variable as our dependent variable, due to the independent variables' high
percentage of correct classifications, we can determine that these variables do in fact predict
heroin death rates in a given county. In addition, since much of the variability is due to the
population of a given county, we can assume that population density is in fact a good predictor
of heroin death rates.  
&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;Therefore, based off of our findings, it is not necessarily true that rural areas,
represented by population density, are more likely to have heroin related deaths. Thus we reject
our null hypothesis and claim that further research must be done in order to determine what
factors to look for when deciding which areas will more likely be effected by heroin use.  

  
##Bibliograph/Works Cited
The Atlantic. Atlantic Media Company, n.d. Web. 07 Dec. 2016.  
"Bureau of Economic Analysis." US Department of Commerce, BEA, Bureau of Economic Analysis.  
&nbsp;&nbsp;&nbsp;N.p., n.d. Web. 07 Dec. 2016.  
Centers for Disease Control and Prevention. Centers for Disease Control and Prevention, 30 Mar.   
&nbsp;&nbsp;&nbsp;2016. Web. 07 Dec. 2016.  
"Drug Overdose Deaths*." County Health Rankings & Roadmaps. N.p., n.d. Web. 07 Dec. 2016.   
"Drug-poisoning Deaths Involving Heroin: United States, 2000-2013." Centers for Disease Control  
&nbsp;&nbsp;&nbsp;and Prevention. Centers for Disease Control and Prevention, 04 Mar. 2015. Web. 07 Dec. 2016.  
"Local Area Unemployment Statistics Home Page." U.S. Bureau of Labor Statistics. U.S. Bureau of  
&nbsp;&nbsp;&nbsp;Labor Statistics, n.d. Web. 07 Dec. 2016.  
Secretary, HHS Office of the. "Opioids: The Prescription Drug & Heroin Overdose Epidemic."  
&nbsp;&nbsp;&nbsp;HHS.gov. N.p., 24 Mar. 2016. Web. 07 Dec. 2016.
